signalHsmm with k-mer hidden states

### 2015-06-19 signalHSMM_kMer_report.Rmd
updating benchmark to include model with k-mers

# usuniecie 4 obserwacji negatywnych
negs <- c(432, 215, 280, 417)
# negs <- sample(215:432, 4)
# [1] 432 215 280 414
benchmark_data2 <- benchmark_data2[-negs]
other_soft <- other_soft[-negs,]
real_labels <- c(rep(1, 214), rep(0, 214))
```

>>>>

# usuniecie 4 obserwacji negatywnych
negs <- c(432, 215, 280, 417)
benchmark_data2 <- benchmark_data2[-negs]
other_soft <- other_soft[-negs,]
real_labels <- c(rep(1, 214), rep(0, 214))
```
